---
title: "STA304 Marriage License Statistics in 2024"
author: 
  - He Tianning
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "Research the number of Marriage License Statistics in 2024 ."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

```


# Introduction

we Research the number of Marriage License Statistics in 2024, and use the data to get the distribution of that.


# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

data |> 
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point()+labs(title = "Distribution of Toronto Marriage in 2024",
                    x = "Date", 
                    y = "Marriage License")
```



# Results

The graph above shows the distribution of the marriage licences.



# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional data details




\newpage


# References

url ={https://open.toronto.ca/dataset/marriage-licence-statistics/}
